Type Ia Supernova Explosions from Hybrid Carbon-Oxygen-Neon White Dwarf Progenitors

### 2019-02-09 paper/ms.tex
Even more on Carlyn's paper. Getting thorough the methodology

The hybrid white dwarf model that served as the initial conditions 
for the simulations of supernova explosions presented in this work
was constructed with the one-dimensional stellar evolution code 
MESA~\citep{mesa1,mesa2,mesa3,mesa3e}. The evolution of the model 
included thermohalene mixing during the cooling phase and thus
had a lower C fraction than previous hybrid models~\citep{brooksetal2017}.
The hybrid model was constructed to have conditions as similar a possible
to a ``classic" C/O model and the two shared the same central temperature
and density.  Figure~\ref{fig:init_conds} shows the density and temperature
profiles of the two initial one-dimensional models. 
\begin{figure}
\includegraphics[width=\columnwidth]{figures/initial_conds.png}
\caption{\label{fig:init_conds}
Temperature, density, and  composition profiles of the one-dimensional hybrid 
progenitor WD. The central temperature and density were the same as
the tradtional C/O progenitor model. 
 We found that the most abundant isotopes in the model were C12, O16, Ne20. There were a few other isotopes that were added to form Ne22 later. We saw that  ….
Plotting the density verses solar radii, we found that the densest part of the star is in the center slowly decreasing until it hits 0 at the outer edge of the star. 
In order to see where we should ignite the flame, we plotted the temperature profile. It was found that the peak temperature is at the center of the star, therefore, it was obvious to ignite the flame in the core. (PUT IN TEMP PROFILE)
}
\end{figure}
In both models, and unlike the hybrid models of~\citet{willcoxetal2016}, the central
temperature was the highest at the center of the star and accordingly the simulations 
began with central initions.

@@

The initial progenitor models for the two-dimensional simulations were
created from the one-dimensional \MESA models by mapping the one-dimensional
models onto the two-dimensional domain while 
preserving hydrostatic equilibrium.
As described above, the flame capturing scheme with progress
variables describing the evolution as the material burns. The \MESA
models, however, relied on a detailed reaction network that included
many species. Accordingly, the process of creating the two-dimensional
models for \FLASH required aggregating some of the species abundances.
As with much of this study, we applied the 
techniques of ~\citet{willcoxetal2016}.

The process of mapping the \MESA models began by converting 
the \MESA\ model to a uniform grid of $4$~km resolution. \MESA 
quantities in zones with spacing less than $4$~km 
were mass-weighted averaged and a quadratic interpolation
was used to calculate quantities for the case of \MESA zones having
a spacing greater than $4$~km. At this point, 
abundances of nuclides from the \MESA models were aggregated
into abundances of

representing neutron-rich metals were aggregated into

a variable representing

An additional step in constructing the two-dimensional initial conditions
was aggregating nuclides representing neutron-rich metals. 
The most abundant isotopes in the model were C12, O16,
Ne20 CHECK NE@) IS SYMMETRIC, which are symmetric (the number of neutrons 
equals the number of protons). Similarly to~\citet{willcoxetal2016}, other 
neutron-rich isotopes in
the initial model were to form Ne22, which serves as a proxy for metallicty. 
MESA model into FLASH, which is a 2-D code, we needed symmetric nuclear
matter. This means that the ratio of neutrons to protons in the nuclei
must be the same ratio as in the mesa profile. This is because the amount
of extra neutrons around is important when burning the star because that
determines how much neutron rich isotopes the burning produces.

>>>>

The hybrid white dwarf model that served as the initial conditions 
for the simulations of supernova explosions presented in this work
was constructed with the one-dimensional stellar evolution code 
MESA~\citep{mesa1,mesa2,mesa3,mesa3e}. The evolution of the model 
included thermohalene mixing during the cooling phase and thus
had a lower C fraction than previous hybrid models~\citep{brooksetal2017}.
The hybrid model was constructed to have conditions as similar a possible
to a ``classic" C/O model and the two shared the same central temperature
and density.  Figure~\ref{fig:init_conds} shows the density and temperature
profiles of the two initial one-dimensional models. 
\begin{figure}
\includegraphics[width=\columnwidth]{figures/initial_conds.png}
\caption{\label{fig:init_conds}
Temperature, density, and  composition profiles of the one-dimensional hybrid 
progenitor WD. The central temperature and density were the same as
the tradtional C/O progenitor model. 
The peak temperature of the hybrid model is at the center of the star, 
so both the hybrid and traditional models could share the same 
	central ignition initial conditions.
}
\end{figure}
In both models, and unlike the hybrid models of~\citet{willcoxetal2016}, the central
temperature was the highest at the center of the star and accordingly the simulations 
began with central ignitions.

@@

The initial progenitor models for the two-dimensional simulations were
created from the one-dimensional \MESA\ models by mapping the one-dimensional
models onto the two-dimensional domain while 
preserving hydrostatic equilibrium.
As described above, the flame capturing scheme with progress
variables describing the evolution as the material burns. The \MESA\
models, however, relied on a detailed reaction network that included
many species. Accordingly, the process of creating the two-dimensional
models for \FLASH\ required aggregating some of the species abundances.
As with much of this study, we applied the 
techniques of ~\citet{willcoxetal2016}.

The process of mapping the \MESA\ models began by converting 
the \MESA\ model to a uniform grid of $4$~km resolution. \MESA\ 
quantities in zones with spacing less than $4$~km 
were mass-weighted averaged and a quadratic interpolation
was used to calculate quantities for the case of \MESA\ zones having
a spacing greater than $4$~km. At this point, 
abundances of nuclides from the \MESA\ models were aggregated
into the abundances tracked by the flame capturing scheme in
\FLASH.
The most abundant isotopes in the model were \C{12}, \Ox{16},
and \Ne{20}, which are symmetric (the number of neutrons 
equals the number of protons). Similarly to~\citet{willcoxetal2016}, 
other neutron-rich isotopes in the initial model were combined into 
\Ne{22}, which serves as a proxy for metallicty. The aggregation
account for the $Y_e$ of the full set of nuclides, \Ne{20} 
and \Ox{16} were constrained to be in the same ratio $R$ in both 
sets of abundances.

MESA model into FLASH, which is a 2-D code, we needed symmetric nuclear
matter. This means that the ratio of neutrons to protons in the nuclei
must be the same ratio as in the mesa profile. This is because the amount
of extra neutrons around is important when burning the star because that
determines how much neutron rich isotopes the burning produces.
